---
title: "Generate normal distribution from cauchy and laplace disdtribution"
author: "Parnian Jahangiri Rad"
date: "2/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

student number:9813007  
  
### Generate normal random numbers using cauchy distribution:  
```{r,message=FALSE,warning=FALSE}
set.seed(666)
n <- 10000
c1 <- 1.52
repeat1 <- 0
x1 <- rep(0,n)
for (i in 1:n){
repeat{
repeat1 <- repeat1 + 1
y1 <- rcauchy(1)
u1 <- runif(1,0,1)
if(u1 < (dnorm(y1) /(c1 * dcauchy(y1)))) break
}
x1[i] <- y1
}

hist(x1)
summary(x1)
```

```{r,message=FALSE,warning=FALSE}
#qqplot:
set.seed(666)
norm10000 <- rnorm(10000)
qqplot(norm10000,x1)
```

Probability of acceptance in acceptance-rejection method is 1/c:  
```{r,message=FALSE,warning=FALSE}
#Probability of acceptance of generating normal from cauchy:
p1 <- 1/c1
p1
```

### Generate normal random numbers using laplace distribution:  
```{r,message=FALSE,warning=FALSE}
library(ExtDist)
set.seed(666)
n <- 10000
c2 <- 1.3
repeat2 <- 0
x2 <- rep(0,n)
for(i in 1:n){
repeat{
repeat2 <- repeat2 + 1
y2 <- rLaplace(1)
u2 <- runif(1,0,1)
if(u2 < (dnorm(y2) /(c2 * dLaplace(y2)))) break
}
x2[i] <- y2
}
hist(x2)
summary(x2)
```

```{r,message=FALSE,warning=FALSE}
#qqplot:
qqplot(norm10000,x2)
```

Probability of acceptance in acceptance-rejection method is 1/c:  
```{r,message=FALSE,warning=FALSE}
#Probability of acceptance of generating normal from cauchy:
p2 <- 1/c2
p2
```

### Cauchy vs Laplace for generating normal random number  
Based on `p1` and `p2`, we can say that laplace distribution is a better choice for generating random
numbers from normal distribution.
We can also tell it based on `repeat1` and `repeat2`:
```{r,message=FALSE,warning=FALSE}
#number of iterations to generate 10000 normal random numbers from
#cauchy distribution
repeat1
```

```{r,message=FALSE,warning=FALSE}
#number of iterations to generate 10000 normal random numbers from
#laplace distribution
repeat2
```

`repeat2` is less than `repeat1`,so we can say that laplace distribution is a better choice for generating
random numbers from normal distribution.




